Neurology II

### 2017-09-08 neuro2.rmd
updated some typos, hopefully table goes towards the \section

---
title: "Module II"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
urlcolor: blue
---

# Readings

@@

-  Anterolateral tract: spinothalamic (pain and temp), spinoreticular, spinotectal = {pain, temperature, crude touch, firm pressure}
-  Dorsal lemniscal: check lecture 4 of this week (Bellingham)

@@

High doses on muscle: fasciculations $\rightarrow$ inability to repolarise cell membranes $\rightarrow$ weakness + paralysis $\rightarrow$ ventilatory failure $\rightarrow$

@@

Memorise the picture from the Eastern European lecturer.

>>>>

---
title: "Neurology II"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
urlcolor: blue
---

@@

-  Anterolateral tract: spinothalamic (pain and temp), spinoreticular, spinotectal = {pain, temperature, crude touch, firm pressure}. Goes up or down 1 or 2 levels then decussates.
-  Dorsal lemniscal (column): fine touch and proprioception, decussates up in the brainstem.

@@

High doses on muscle: fasciculations $\rightarrow$ inability to repolarise cell membranes $\rightarrow$ weakness + paralysis $\rightarrow$ ventilatory failure $\rightarrow$ death

@@
